---
title: "R Notebook"
output: html_notebook
---

```{r,setup}
library(x3ptools)
library(tidyverse)
library(cmcR)

source("../../cmas Functions/cmasFunctions.R") #new helper functions
```

```{r}
P0010 <- read_x3p(file = "P0010_mask.x3p")

P0011 <- read_x3p(file = "P0011_mask.x3p")
```

```{r}
x3pListPlot(list("P0010" = P0010 %>% sample_x3p(m = 4),
                 "P0011" = P0011 %>% sample_x3p(m = 4)))
```


Preprocess Scans

```{r}
P0010_processed <- P0010 %>%
  x3p_delete(mask_vals = "#CD7F32FF") %>%
  preProcess_removeTrend(statistic = "quantile",
                         tau = .5,
                         method = "fn") %>%
  preProcess_gaussFilter() %>% 
  x3p_sample() %>%
  preProcess_removeTrend(statistic = "quantile",
                         tau = .5,
                         method = "fn") %>%
  preProcess_gaussFilter() %>% 
  x3p_sample() %>%
  cmcR:::preProcess_cropWS()

P0010_processed$mask <- NULL

P0011_processed <- P0011 %>%
  x3p_delete(mask_vals = "#CD7F32FF") %>%
  preProcess_removeTrend(statistic = "quantile",
                         tau = .5,
                         method = "fn") %>%
  preProcess_gaussFilter() %>% 
  x3p_sample() %>% 
  preProcess_removeTrend(statistic = "quantile",
                         tau = .5,
                         method = "fn") %>%
  preProcess_gaussFilter() %>% 
  x3p_sample() %>%
  cmcR:::preProcess_cropWS()

P0011_processed$mask <- NULL

x3pListPlot(list("P0010 Processed" = P0010_processed,
                 "P0011 Processed" = P0011_processed))
```

Calculate similarity features between the two scans
```{r}
comparisonData <- purrr::map_dfr(seq(-30,30,by = 3),
                                 ~ comparison_allTogether(reference = P0010_processed,
                                                          target = P0011_processed,
                                                          theta = .,
                                                          numCells = 64,
                                                          maxMissingProp = .85))
```


Launch shiny app. May take a sec to load since the polar domain estimated rotation is calculated first.

(To-do: remove excess white space around plots to avoid overlapping. Alternatively, move difference plot to a different part of the page.)

```{r}
estimatedRotationApp(reference = P0010_processed,
                     target = P0011_processed,
                     reference_v_target_comparison = comparisonData)
```

```{r}
alignedScans <- alignScans(P0010_processed,P0011_processed,differences = "do nothing")


pltDat <- bind_rows(alignedScans[[1]] %>%
                      x3pToDF() %>%
                      mutate(x3pName = "P0010"),
                    alignedScans[[2]] %>%
                      x3pToDF() %>%
                      mutate(x3pName = "P0011"))  %>%
  pivot_wider(id_cols = c(x,y,x3pName),names_from = x3pName,values_from = value)  %>%
  mutate(difference = P0010 - P0011)
  # mutate(difference = purrr::map2(P0010,P0011,
  #                                 ~ sum(.x,-1*.y,
  #                                       na.rm = TRUE)) %>% 
  #          unlist())

pltDat %>%
  ggplot(aes(x = x,y = y,fill = difference)) +
  geom_raster() +
  ggplot2::scale_fill_gradientn(colours = rev(c('#7f3b08','#b35806','#e08214','#fdb863','#fee0b6','#f7f7f7',
                                                '#d8daeb','#b2abd2','#8073ac','#542788','#2d004b')),
                                values = scales::rescale(quantile(pltDat$difference,
                                                                  c(0,.01,.025,.1,.25,.5,.75,0.9,.975,.99,1),
                                                                  na.rm = TRUE)),
                                breaks = function(lims){
                                  dat <- quantile(as.vector(pltDat$difference),
                                                  c(0,.01,.5,.99,1),
                                                  # c(0,.01,.025,.1,.25,.5,.75,0.9,.975,.99,1),
                                                  na.rm = TRUE)
                                  
                                  dat <- dat %>%
                                    setNames(paste0(names(dat)," [",round(dat*1e6,1),"]"))
                                  
                                  return(dat)
                                },
                                na.value = "transparent",
                                guide = ggplot2::guide_colorbar(title = expression("Rel. Height ["*mu*"m]"),
                                                                barheight = 10,
                                                                order = 1,
                                                                label.theme = ggplot2::element_text(size = 8),
                                                                title.theme = ggplot2::element_text(size = 10))) +
  ggplot2::coord_fixed(expand = FALSE) +
  ggplot2::theme_minimal() +
  ggplot2::scale_y_reverse() +
  ggplot2::theme(axis.ticks.x = ggplot2::element_blank(),
                 axis.ticks.y = ggplot2::element_blank(),
                 panel.grid.major = ggplot2::element_blank(),
                 panel.grid.minor = ggplot2::element_blank(),
                 panel.background = ggplot2::element_blank())
```


Try again with a P0011 scans with a new mask including more of the breech face near the firing pin "tongue mark". This doesn't seem to affect the Original Method or High CMC Method estimated rotation, but slightly changes the polar domain estimated rotation

```{r}
P0011 <- read_x3p(file = "P0011_mask_new.x3p")

P0011_processed_new <- P0011 %>%
  x3p_delete(mask_vals = "#CD7F32FF") %>%
  preProcess_removeTrend(statistic = "quantile",
                         tau = .5,
                         method = "fn") %>%
  preProcess_gaussFilter() %>% 
  x3p_sample() %>% 
  preProcess_removeTrend(statistic = "quantile",
                         tau = .5,
                         method = "fn") %>%
  preProcess_gaussFilter() %>% 
  x3p_sample() %>%
  cmcR:::preProcess_cropWS()

P0011_processed_new$mask <- NULL

comparisonData2 <- purrr::map_dfr(seq(-30,30,by = 3),
                                  ~ comparison_allTogether(reference = P0010_processed,
                                                           target = P0011_processed,
                                                           theta = .,
                                                           numCells = 64,
                                                           maxMissingProp = .85))

estimatedRotationApp(reference = P0010_processed,
                     target = P0011_processed_new,
                     reference_v_target_comparison = comparisonData2)
```

